peter_models

### 2024-12-14 peter_models.qmd
updating plot to label y aaxis variables

>>>>

# Testing plotting function
```{r}
or_data_test <- exp(cbind(OR=coef(ord_mod_interactions),confint(ord_mod_interactions)))

  # Calculate p-values
p_values_test <- pnorm(-abs(summary(ord_mod_interactions)$coefficients[,"t value"]))*2

  # Keep only significant variables
sig_indices_test <- p_values_test[names(coef(ord_mod_interactions))] < 0.05
or_data_sig_test <- or_data_test[sig_indices_test, ]

rename_map <- c(
    "Q271_reordered(2) Very important" = "Racial Belonging - Very Important",
    "Q271_reordered(1) Extremely important" = "Racial Belonging - Extremely Important",
    "S3B(2) Woman" = "Gender - Woman",
    "S3B(3) Non-binary" = "Gender - Non-binary",
    "race_recodedBlack" = "Race - Black",
    "race_recodedAsian American" = "Race - Asian",
    "race_recodedLatino" = "Race - Latino",
    "race_recodedAIAN" = "Race - Native",
    "race_recodedNHPI" = "Race - NHPI",
    "age_recoded50-59" = "Age - 50-59",
    "age_recoded60-69" = "Age - 60-69",
    "age_recoded70+" = "Age - 70+",
    "educSome college experience" = "Education - Some College",
    "educCollege graduate" = "Education - College Graduate",
    "Q21(2) Democrat" = "Party ID - Democrat",
    "Q21(3) Independent" = "Party ID - Independent",
    "Q21(4) Other party" = "Party ID - Other",
    "Q271_reordered(1) Extremely important:S3B(2) Woman" = "Interaction: Racial Belonging & Gender: Woman"
  )

rownames(or_data_sig_test) <- rename_map[rownames(or_data_sig_test)]

or_data_sig_test

# Trying to run the plot again but with explicit y-axis Variable labels

```{r}
odds_ratio_plot_labelled <- function(model) {
  # Get odds ratios and CIs
  or_data <- exp(cbind(OR=coef(model),confint(model)))

  rename_map <- c(
    "Q271_reordered(2) Very important" = "Racial Belonging - Very Important",
    "Q271_reordered(1) Extremely important" = "Racial Belonging - Extremely Important",
    "S3B(2) Woman" = "Gender - Woman",
    "S3B(3) Non-binary" = "Gender - Non-binary",
    "race_recodedBlack" = "Race - Black",
    "race_recodedAsian American" = "Race - Asian",
    "race_recodedLatino" = "Race - Latino",
    "race_recodedAIAN" = "Race - Native",
    "race_recodedNHPI" = "Race - NHPI",
    "age_recoded50-59" = "Age - 50-59",
    "age_recoded60-69" = "Age - 60-69",
    "age_recoded70+" = "Age - 70+",
    "educSome college experience" = "Education - Some College",
    "educCollege graduate" = "Education - College Graduate",
    "Q21(2) Democrat" = "Party ID - Democrat",
    "Q21(3) Independent" = "Party ID - Independent",
    "Q21(4) Other party" = "Party ID - Other",
    "Q271_reordered(1) Extremely important:S3B(2) Woman" = "Interaction: Racial Belonging & Gender: Woman"
  )
  or_data_sig_renamed <- or_data_sig
  rownames(or_data_sig_renamed) <- rename_map[rownames(or_data_sig_renamed)]

  ggplot() +
    # Add vertical line at OR = 1
    geom_vline(xintercept = 1, linetype = "dashed", color = "red", size = 0.7) +
    # Add points and error bars
    geom_point(aes(x = or_data_sig_renamed[,1], 
                   y = reorder(rownames(or_data_sig_renamed), or_data_sig_renamed[,1])), 
              size = 4, color = "blue") +
    geom_errorbarh(aes(xmin = or_data_sig[,2], 
                       xmax = or_data_sig[,3],
                       y = reorder(rownames(or_data_sig_renamed), or_data_sig_renamed[,1])),
                   height = 0.3, color = "black") +
    # Customize theme
    theme_minimal() +
    theme(
      axis.text.y = element_text(size = 6, color = "black"),
      axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
      axis.title.x = element_text(size = 12, face = "bold"),
      axis.title.y = element_text(size = 12, face = "bold"),
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      plot.margin = margin(1, 1, 1, 1, "cm"),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 9)
    ) +
    # Add labels
    labs(
      title = "Significant Variables with Confidence Intervals",
      x = "Odds Ratio",
      y = "Variables"
    )

}

# Generate the plot
odds_ratio_plot_labelled(ord_mod_interactions)
